A thesis draft

### 2018-10-10 draft.tex
Fix repetition

\subsubsection{Other technologies}\todo{Talk somehow of the other tecnhologies}
\paragraph{Openvswitch}
\paragraph{Openbaton} Created by the Institute Fraunhofer, it's a open-source, 
customizable NFV MANO-compliant framework, that offers many configurations 
options, and since it's written in Java, there is the possibility to add 
components (plug-ins) dynamically. Openbaton can be installed as a normal 
computer program (they offer packages for the most common distros) but it can 
be deployed on Docker containers too. It's designed to work with cloud 
providers like Amazon or Google Compute engine, but it offers compability with 
on-permise cloud solutions like Openstack, where it deploys virtual machines 
using the API the platform offers. It can store VNF configurations saved as 
TOSCA YAML\todo{What does TOSCA mean? Find out} and it can handle multiple 
PoPs\todo{Write down PoP meaning}. It offers a VNF lifecyle management 
out-of-the-box, with the possibility to customize it based on the user needs. 
Its modular design allows developers to change parts of the codebase with 
custom ones, making the product really flexible to different platforms. 
Performing this operation requires a deep knowlege of the framework though.
\begin{figure}[h]
 \centering
 \includegraphics[scale=0.45]{openbaton_logo}
 \caption{Openbaton logo}
 \label{chap:prjan:img:openbaton_logo}
\end{figure}

>>>>

\subsubsection{Other technologies}\todo{Talk somehow of the other tecnhologies}
\paragraph{Openvswitch}
\paragraph{Openbaton} Patrocined by the Institute Fraunhofer, it's a 
open-source, customizable NFV MANO-compliant framework, that offers many 
configurations options, and since it's written in Java, there is the possibility 
to add components (plug-ins) dynamically. Openbaton can be installed as a 
normal computer program (they offer packages for the most common distros) but it 
can be deployed on Docker containers too. It's designed to work with cloud 
providers like Amazon or Google Compute engine, but it offers compability with 
on-permise cloud solutions like Openstack, where it deploys virtual machines 
using the API the platform offers. It can store VNF configurations saved as 
TOSCA YAML\todo{What does TOSCA mean? Find out} and it can handle multiple 
PoPs\todo{Write down PoP meaning}. It offers a VNF lifecyle management 
out-of-the-box, with the possibility to customize it based on the user needs. 
Its modular design allows developers to change parts of the codebase with 
custom ones, making the product really flexible to different platforms. 
Performing this operation requires a deep knowlege of the framework though.
\begin{figure}[h]
 \centering
 \includegraphics[scale=0.45]{openbaton_logo}
 \caption{Openbaton logo}
 \label{chap:prjan:img:openbaton_logo}
\end{figure}
